Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-07-12 appendix-EPQ.tex
modify

We generate register automata $\mathcal{A}_{\textit{SinPri}}^1$ for the first case, and it is shown in \figurename~\ref{fig:automata for FIFO-1 in appendix}. Here $C_1 = \{ \textit{call}(\textit{put},a,\textit{true})$, $\textit{ret}(\textit{put},a,\textit{true}), \textit{call}(\textit{rm},a),\textit{ret}(\textit{rm},a),\textit{call}(\textit{rm},b),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty}) \}$, $C_2$ $= C_1 \cup \{ \textit{ret}(\textit{rm},b) \}$, $C_3 = C_2 \cup \{ \textit{ret}(\textit{put},b,\textit{true}) \}$.

@@

We generate register automata $\mathcal{A}_{\textit{SinPri}}^2$ for the second case, and it is shown in \figurename~\ref{fig:automata for FIFO-2}. Here $C_1 = \{ \textit{call}(\textit{put},a,\textit{true}),\textit{ret}(\textit{put},a,\textit{true}), \textit{call}(\textit{rm},a),\textit{ret}(\textit{rm},a),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty}) \}$, $C_2 = C_1 \cup \{ \textit{call}(\textit{rm},b) + \textit{ret}(\textit{rm},b) \}$.

@@

We generate register automata $\mathcal{A}_{\textit{SinPri}}^3$ for the third case, and it is shown in \figurename~\ref{fig:automata for FIFO-3}. Here $C_1 = \{ \textit{call}(\textit{put},a,\textit{true}),\textit{ret}(\textit{put},a,\textit{true}), \textit{call}(\textit{rm},a),\textit{ret}(\textit{rm},a),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty}) \}$, $C_2 = C_1 \cup \{ \textit{ret}(\textit{put},b,\textit{true}) \}$, $C_3 = C_2 \cup \{ \textit{ret}(\textit{rm},b) \}$, $C_4 = C_3 \cup \{ \textit{call}(\textit{rm},b) \}$, $C_5 = C_1 \cup \{ \textit{ret}(\textit{rm},b) \}$, $C_6 = C_5 \cup \{ \textit{call}(\textit{rm},b) \}$.

@@

We generate register automata $\mathcal{A}_{\textit{SinPri}}^4$ for the forth case, and it is shown in \figurename~\ref{fig:automata for FIFO-4}. Here $C_1 = C \cup \{ \textit{call}(\textit{rm},b) \}$, and $C_2 = C \cup \{ \textit{ret}(\textit{put},b,=r), \textit{call}(\textit{rm},a), \textit{ret}(\textit{rm},a) \}$, where $C = \{ \textit{call}(\textit{put},d,\textit{true}),\textit{ret}(\textit{put},d,\textit{true}), \textit{call}(\textit{rm},d),\textit{ret}(\textit{rm},d),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty}) \}$.

@@

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] If this is because case $1$, case $2$ or case $3$: $r$ maps $v_b$ into $b$ and maps all other values into $a$.

\item[-] If this is because case $4$: $r$ maps $v_a$ and $v_b$ into $a$ and $b$, respectively, and maps all other values into $d$.
\end{itemize}

>>>>

We generate register automata $\mathcal{A}_{\textit{SinPri}}^1$ for the first case, and it is shown in \figurename~\ref{fig:automata for FIFO-1 in appendix}. Here $A_1 = \{ \textit{call}(\textit{put},\top,\textit{true})$, $\textit{ret}(\textit{put},\top,\textit{true}), \textit{call}(\textit{rm},\top),\textit{ret}(\textit{rm},\top),\textit{call}(\textit{rm},b),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty}) \}$, $A_2$ $= A_1 \cup \{ \textit{ret}(\textit{rm},b) \}$, $C_3 = C_2 \cup \{ \textit{ret}(\textit{put},b,\textit{true}) \}$.

@@

We generate register automata $\mathcal{A}_{\textit{SinPri}}^2$ for the second case, and it is shown in \figurename~\ref{fig:automata for FIFO-2}. Here $A_1 = \{ \textit{call}(\textit{put},\top,\textit{true}),\textit{ret}(\textit{put},\top,\textit{true}), \textit{call}(\textit{rm},\top),\textit{ret}(\textit{rm},\top),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty}) \}$, $A_2 = A_1 \cup \{ \textit{call}(\textit{rm},b), \textit{ret}(\textit{rm},b) \}$.

@@

We generate register automata $\mathcal{A}_{\textit{SinPri}}^3$ for the third case, and it is shown in \figurename~\ref{fig:automata for FIFO-3}. Here $A_1 = \{ \textit{call}(\textit{put},\top,\textit{true}),\textit{ret}(\textit{put},\top,\textit{true}), \textit{call}(\textit{rm},\top),\textit{ret}(\textit{rm},\top),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty}) \}$, $A_2 = A_1 \cup \{ \textit{ret}(\textit{put},b,\textit{true}) \}$, $A_3 = A_2 \cup \{ \textit{ret}(\textit{rm},b) \}$, $A_4 = A_3 \cup \{ \textit{call}(\textit{rm},b) \}$, $A_5 = A_1 \cup \{ \textit{ret}(\textit{rm},b) \}$, $A_6 = A_5 \cup \{ \textit{call}(\textit{rm},b) \}$.

@@

We generate register automata $\mathcal{A}_{\textit{SinPri}}^4$ for the forth case, and it is shown in \figurename~\ref{fig:automata for FIFO-4}. Here $A_1 = A \cup \{ \textit{call}(\textit{rm},b) \}$, and $A_2 = A \cup \{ \textit{ret}(\textit{put},b,\textit{true}), \textit{call}(\textit{rm},a), \textit{ret}(\textit{rm},a) \}$, where $A = \{ \textit{call}(\textit{put},\top,\textit{true}),\textit{ret}(\textit{put},\top,\textit{true}), \textit{call}(\textit{rm},\top),\textit{ret}(\textit{rm},\top),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty}) \}$.

@@

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] If this is because case $1$, case $2$ or case $3$: $r$ maps $v_b$ into $b$ and maps all other values into $\top$.

\item[-] If this is because case $4$: $r$ maps $v_a$ and $v_b$ into $a$ and $b$, respectively, and maps all other values into $\top$.
\end{itemize}
